---
title: "R Markdown and Leaflet"
author: "Yangtaoyuan"
date: "2021/1/10"
output:
  pdf_document: default
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
The report is the first project of the develop data product, and it mainly use the leaflet to feature the map
 
## load liabrary and map
```{r}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map

```

## add markers
Adopating the longitude and latitude to add markers and popo up text by popup argument.
```{r}
my_map <- my_map %>%
  addMarkers(lat=22.9281, lng=113.2755, 
             popup="XinYi Square")
my_map
```

## Map clusters
 the clusters allows users add many markers by addMarkers() function, you will find out individual marker if you zoom in each cluster. 
```{r}
df <- data.frame(lat = runif(500, min = 22.8281, max = 22.9281),
                 lng = runif(500, min = 113.1755, max = 113.2755))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Conclusion 
 For more details about the leaflet package for R visit http://rstudio.github.io/leaflet/.
 
 